\documentclass[12pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{amsmath, amssymb}
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{lipsum}

% Correct path to graphical file configuration (same folder)
\input{includegraphical_file_path}

\onehalfspacing  % line spacing 1.5

% ---------- Title Info ----------
\title{Association Rule Mining and Time Series Forecasting\\
	\large Data Mining -- Homework 1}
\author{
	Mahmoud Sadrian \\ Student ID: 40435336 \\
	\href{https://github.com/mahmoud-sadrian/RetailPatternsForecast}{GitHub Repository}
}
\date{\today}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		This report presents a complete data mining study on a real-world retail transaction dataset, 
		focusing on manual implementation of association rule mining and time series forecasting. 
		The workflow includes extensive data preprocessing, transformation of transactions into a binary basket matrix,
		and implementation of Apriori frequent itemset generation without external libraries. 
		Frequent itemsets, as well as support, confidence, and lift, were computed manually for all one-item 
		and two-item combinations.
		
		Exploratory data analysis (EDA) was conducted using histograms, bar charts, and basket-level statistics
		to better understand product frequencies and co-occurrence patterns. A set of meaningful association rules 
		was extracted and analyzed, with visualizations illustrating support--confidence--lift relationships.
		
		In the second part of the project, a daily revenue time series was constructed and analyzed. A Simple Exponential 
		Smoothing (SES) forecasting model was manually implemented to predict future revenue, and its performance 
		was compared to a naive baseline forecast. The SES model demonstrated superior performance based on RMSE, MAE, 
		and MAPE metrics.
		
		All computations, algorithms, and visualizations were implemented from scratch, ensuring direct understanding 
		of the mathematical and algorithmic foundations of association rule mining and time series forecasting.
	\end{abstract}
	
	% ---------- Sections as modules ----------
	\input{sections/introduction}
	\input{sections/dataset}
	\input{sections/preprocessing}
	\input{sections/eda}
	\input{sections/association_rules}
	\input{sections/time_series}
	\input{sections/conclusion}
	
	% ---------- References ----------
	\begin{thebibliography}{9}
		
		\bibitem{uci}
		UCI Machine Learning Repository: Online Retail Dataset. \\
		\url{https://archive.ics.uci.edu/dataset/352/online+retail}
		
	\end{thebibliography}
	
\end{document}